\begin{enumerate}
    \item History, pertaining to dangers and effects of certain decisions on immigration policy.
    \item The UN's framework and objectives for the goals of refugee immigration.

    Under the general UN assembly, a refugee has the unconditional right to return home.

    \item How NGOs fit into the immigration picture.

    s

    \item How much does immigration cost?

    Typically, the total cost for processing and accommodating asylum seekers can be in the range of €8 000 and €12 0000 per application for the first year, although the figure may be much lower for fast track processing\footnote{http://www.oecd.org/migration/How-will-the-refugee-surge-affect-the-European-economy.pdf -- GOOD ECONOMIC PAPER}. 4 years after social assistance, 75\% of immigrants moved out of social assistance.

    \item Look up the application for official refugee status.

    Look in paper\footnote{$http://fra.europa.eu/sites/default/files/fra-focus_02-2015_legal-entry-to-the-eu.pdf$} and also\footnote{$https://www.hrw.org/report/2015/11/16/europes-refugee-crisis/agenda-action$}.

    The first step for a refugee is to arrive and register in a UNHCR refugee camp outside of Syria. The UNHCR then refers those who pass the first stage of vetting to the U.S. government refugee process (as described above). The National Counterterrorism Center, the Terrorist Screening Center, the Department of Defense, the FBI, Department of Homeland Security, and the State Department use biometrics and biographical information gleaned through several interviews of the refugee and third-party persons who know him or could know him to make sure applicants really are who they claim to be, to evaluate their security risk, and to investigate whether they are suspected of criminal activity or terrorism.  Numerous medical checks are also performed.  During this entire screening process, which takes about three years for Syrians, the refugee has to wait in the camp. If there is any evidence that the refugee is a security threat, he or she is not allowed to come to the United States\footnote{http://www.cato.org/blog/syrian-refugees-dont-pose-serious-security-threat}.

    \item How many immigrants do we need to accomodate?

    3 Million refugees to enter the EU by the end of 2016\footnote{http://www.independent.co.uk/news/world/europe/eu-expecting-another-3-million-refugees-migrants-before-end-of-2016-a6722096.html}.

    \item What Routes do immigrants take - what type of transportation are they taking?

    \item Where are immigrants trying to go?

    \item Quotas for countries.
\end{enumerate}

\begin{enumerate}
    \item The majority of refugees resettle in the middle eastern countries of Jordan, Lebanon, and Turkey.
    \item 1,015,078 refugees arrived by sea in 2015.
    \item 942,000 refugees sought asylum in the European Union in 2015\footnote{Eurostat}.
    \item 315,000 have sought asylum in Germany, yet more than 1 million have been counted in Germany's EASY system\footnote{http://www.bbc.com/news/world-europe-34131911}.
    \item 174,055 applied in Hungary.
\end{enumerate}

$http://www.pewresearch.org/fact-tank/2015/04/24/refugees-stream-into-europe-where-they-are-not-welcomed-with-open-arms/ft_15-04-22_eu-immigration/$

